Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*

### 2022-11-16 reports/supplement/supplement_0.9.1.Rmd
First attempt at #27 https://github.com/UZH-PEG/diversity_envresp1/issues/27

>>>>

# ADDED BY RAINER Issue #27

## 
```{r}

## PB
only_PB_variable <- ss_9s %>%
  filter(
    abs(CB_var_gmax_s) < 0.0001,
    abs(SB_var_gmax_s) < 0.0001
  )
only_PB_variable <- only_PB_variable[order(only_PB_variable$PB_var_gmax_s), ]

## CB
only_CB_variable <- ss_9s %>%
  filter(
    abs(PB_var_gmax_s) < 0.0001,
    abs(SB_var_gmax_s) < 0.0001
  )
only_CB_variable <- only_CB_variable[order(only_CB_variable$CB_var_gmax_s), ]

## SB
only_SB_variable <- ss_9s %>%
  filter(
    abs(PB_var_gmax_s) < 0.0001,
    abs(CB_var_gmax_s) < 0.0001
  )
only_SB_variable <- only_SB_variable[order(only_SB_variable$SB_var_gmax_s), ]

## PB_CB
only_PB_CB_variable <- ss_9s %>%
  filter(
    abs(SB_var_gmax_s) < 0.0001
  )
only_PB_CB_variable <- only_PB_CB_variable[order(only_PB_CB_variable$PB_var_gmax_s), ]

## CB_SB
only_CB_SB_variable <- ss_9s %>%
  filter(
    abs(PB_var_gmax_s) < 0.0001
  )
only_CB_SB_variable <- only_CB_SB_variable[order(only_CB_SB_variable$PB_var_gmax_s), ]

## PB_SB
only_PB_SB_variable <- ss_9s %>%
  filter(
    abs(CB_var_gmax_s) < 0.0001
  )
only_PB_SB_variable <- only_PB_SB_variable[order(only_PB_SB_variable$PB_var_gmax_s), ]

## CB_PB_SB
only_CB_PB_SB_variable <- ss_9s
only_CB_PB_SB_variable <- only_CB_PB_SB_variable[order(only_CB_PB_SB_variable$PB_var_gmax_s), ]

## PB
```{r echo = FALSE,  include=TRUE, fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(only_PB_variable[sim1,])
fig_state_vs_o2diff_sidebyside_alternative(only_PB_variable[sim2,])
```

## CB
```{r echo = FALSE,  include=TRUE, fig.height=10, fig.width=8, fig.align="center"}
sim3 <- 19
fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[sim1,])
fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[sim2,])
fig_state_vs_o2diff_sidebyside_alternative(only_CB_variable[sim3,])
```

## SB
```{r echo = FALSE,  include=TRUE, fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[sim1,])
fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[sim2,])
```

## PB & CB
```{r echo = FALSE,  include=TRUE, fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(only_PB_CB_variable[sim1,])
fig_state_vs_o2diff_sidebyside_alternative(only_PB_CB_variable[sim2,])
```

## CB & SB
```{r echo = FALSE,  include=TRUE,, fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(only_CB_SB_variable[sim1,])
fig_state_vs_o2diff_sidebyside_alternative(only_CB_SB_variable[sim2,])
```

## PB & SB
```{r echo = FALSE,  include=TRUE, fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(only_PB_SB_variable[sim1,])
fig_state_vs_o2diff_sidebyside_alternative(only_PB_SB_variable[sim2,])
```

## CB & PB & SB
```{r echo = FALSE,  include=TRUE, fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(only_CB_PB_SB_variable[sim1,])
fig_state_vs_o2diff_sidebyside_alternative(only_CB_PB_SB_variable[sim2,])
```
